### 2025-07-30 response.tex

As the reviewers note ``an
implementation that does not finalize anything would be compliant when
finalization may be deferred indefinitely'' is true of most GCed
implementations we are aware of, including Java. Indeed, Java once had the
\lstinline{runFinalizersOnExit} flag to force finalizers to be run before the
JVM exists; it was long marked as deprecated as ``inherently unsafe'' and
now appears to have been removed; instead,
there is now the \lstinline{addShutdownHook} mechanism.

While investigating this further, we discovered one surprise (to us, at least),
which muddies the waters with respect to finalizer latency further. In Rust,
when a thread unwinds (i.e.~panics) then, depending on compile-time flags, no
destructors will be run --- but Alloy can run all of the `queued' finalizers!
We have not belaboured this point in the paper, but it shows that destructors
can have guaranteed-infinite latency in some situations where finalizers have
infinite-at-worst latency.

\subsection*{Performance Evaluation}

We have made a large number of changes to the performance evaluation. These are
mostly due to reviewer comments, but we also uncovered a mistake in our
experiment. We previously used \boehm's \lstinline{GC_heapsize} metric:
this does not, as we assumed, represent current heap usage, but total
memory usage since the program's start. We now use the \lstinline{GC_bytes_allocd} metric,
which does measure the correct thing. This changes the results for finalizer
elision in one way: previously this appeared to cause heap usage to grow, but in
fact it shrinks.

@@

The most significant changes are:

\begin{itemize}
  \item We provide a comparison of \lstinline{Rc<T>} with jemalloc and \boehm
    in Table~4 in the Appendix. This suggests that the inherent
    overhead of \boehm ranges from 2--26\%, averaging around 11\%.
